%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape John Dilger} \\ \vspace{1pt}
    \small 831-676-6111 $|$ \href{mailto:johnjdilger@gmail.com}{\underline{johnjdilger@gmail.com}} $|$ 
    \href{https://linkedin.com/in/john-dilger}{\underline{linkedin.com/in/john-dilger}} $|$
    \href{https://github.com/jdilger}{\underline{github.com/jdilger}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of San Francisco}{San Francisco, CA}
      {Bachelor of Science in Environmental Science}{2013 -- 2016}
    \resumeSubheading
      {University of San Francisco}{San Francisco, CA}
      {Graduate Geospatial Technology Certification}{2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sr. Data Scientist}{2022 -- 2024}
      {Astraea}{Remote - Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed production analytics for road segmentation, forest loss, construction monitoring, and substation identification. Tech: Python, PyTorch, GDAL, Docker}
        \resumeItem{Developed 20+ pipelines for ML batch prediction, ETL, and model training. Tech: Metaflow, Argo, Docker, Python}
        \resumeItem{Developed internal tools for managing and updating data science databases. Tech: Python, Postgresql/PostGIS}
        \resumeItem{Improved query time for utility owned property analytic. Reduced query time from ~25 minutes to ~2 seconds for parcel table spanning 155MM records. Tech: Postgresql/PostGIS}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
    % \resumeSubSubheading
    %   {Software Engineer I}{Oct 2014 - Sep 2016}
    %   \resumeItemListStart
    %     \resumeItem{Apache Beam}
    %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
    %   \resumeItemListEnd
    % % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Geospatial Data Scientist}{2018 -- 2022}
      {Spatial Informatics Group}{Remote - San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Created insights and automated workflows for forest carbon monitoring, restoration planning, and forest monitoring reporting and validation. Tech: Google Earth Engine, Python, GIS, SQL}
        \resumeItem{Researched and developed geospatial applications using computer vision for areas of crop mapping, invasive species detection, and illegal gold mining. Tech: Tensorflow, Google Earth Engine, Python, Google Cloud Platform}
        \resumeItem{Created ETL pipelines for batch data ingestion/export from Google Earth Engine. Tech: Python, Google Storage, Google Earth Engine}
        \resumeItem{Manage IAM and resources for the Environmental Mapping team. Tech: Google Cloud Platform}
      \resumeItemListEnd

    \resumeSubheading
      {Geoinformatic Fellowship}{2017 -- 2018}
      {NASA DEVELOP National Program - SSA}{Moffit Field, CA}
      \resumeItemListStart
        \resumeItem{Served as point of contact for GIS -ArcMap, ENVI, QGIS-, remote sensing, and scripting -Python, JavaScript- needs for ~50 NASA DEVELOP project teams as part of a 3 person team.}
        \resumeItem{Directly collaborated with Ames Research Center DEVELOP project teams processing multispectral remotely sensed imagery -Landsat, RapidEye, Sentinel-2- and supporting geospatial analysis.}
        \resumeItem{Managed software release process of 5 project teams.}
        \resumeItem{Managed NASA DEVELOP Google Earth Engine repository and helped manage NASA DEVELOP GitHub.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Earth Science Contractor}{2017}
  % \resumeSubHeadingListEnd

  \resumeSubheading
  {LiDAR and Geospatial Analyst Volunteer}{2016 -- 2017}
  {University of San Francisco Geospatial Analysis Lab}{San Francisco, CA}
  % \resumeItemListStart
  %   \resumeItem{Served as point of contact for GIS -ArcMap, ENVI, QGIS-, remote sensing, and scripting -Python, JavaScript- needs for ~50 NASA DEVELOP project teams as part of a 3 person team.}
  %   \resumeItem{Directly collaborated with Ames Research Center DEVELOP project teams processing multispectral remotely sensed imagery -Landsat, RapidEye, Sentinel-2- and supporting geospatial analysis.}
  %   \resumeItem{Managed software release process of 5 project teams.}
  %   \resumeItem{Managed NASA DEVELOP Google Earth Engine repository and helped manage NASA DEVELOP GitHub.}
  % \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Se.plan} $|$ \emph{Python, Google Earth Engine, ipyvuetify}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Application for planning forest restoration activities based upon user constraints, restoration goals, and cost for low and middle-income countries.}
            \resumeItem{Developed core code for analysis and dashboard using Google Earth Engine Python API.}
            \resumeItem{Assisted in front-end development using Jupyter notebooks, Voila, and Ipyvueify.}
            \resumeItem{Application is hosted on the U.N. Food and Agriculture SEPAL platform}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Post Fire Vegetation Monitoring Plumas County, USA} $|$ \emph{Python, Google Earth Engine, Django}}{May 2018 -- May 2020}
          \resumeItemListStart
            \resumeItem{DThis system provides land managers systematic updates for areas burned by wildfire, including changes in vegetation cover on a yearly cadence from 1984 onward.}
            \resumeItem{Wrote image preprocessing and analysis using Google Earth Engine Python API.}
            \resumeItem{Maintained and updated front-end Django website over 2 years.}
            \resumeItem{Landcover classification was done using a random forest, trained on multi year features, and had an $R^2$ of 0.87.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}